### 2014-11-12 tex/heap.tex
Reworked section 2.2. opening paragraph

\subsection{Summary Heaps as Bipartite Graphs}
An important part and novel contribution of summary heaps for symbolic
execution is the labeled bipartite graph representation of the heap
which enables a summary heap to group heaps together that follow the
same control flow to a given point of execution. The group of heaps
split depending on control flow branches: heaps in the original group
that follow a true outcome form a new group while heaps from that same
original group that follow a false outcome form a different
group. State explosion in symbolic execution is thus mitigated by
storing a group of heaps in the state and only branching when that
group splits.

>>>>

\subsection{Summary Heaps as Bipartite Graphs}
A novel contribution of summary heaps for symbolic execution is the
labeled bipartite graph representation of the heap which enables a
summary heap to group heaps together that follow the same control flow
to a given point of execution. The graph structure is able to capture
group membership and compute value sets using entirely non-recursive
local look up. Additionally, updates on the heap do not require
rewriting the path condition or any constraints in the heap.
